EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-07-15 05_examples.tex
CMake options have changed. Updated table

   !Solver-specific arrays. Using Rank-5  
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Construct Bethe DOS using SciFortran
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,Wband)*de
   !
   !EDIpack: Set impurity Hamiltonian
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;

@@

//Locally defined functions:
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,Wband,de);

@@

The first two steps are handled directly by \NAME routines, while during the subsequent steps the 
 control returns to the user, who must implement the algebraic updates required to 
close the self-consistency loop and optimize the bath.
Given the 
critical importance of this optimization, \NAME provides access to 
well-tested functions, ensuring stability and reproducibility of 
results. Alternative optimization methods can also be employed as 
needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
An example of implementation is provided in the following listings.

>>>>

   !Solver-specific arrays. Using Rank-5  
   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
   allocate(Hloc(Nspin,Nspin,Norb,Norb))
   Hloc=0d0
   !...
   !Construct Bethe DOS using SciFortran
   !de = 2*D/Le
   allocate(Ebands(Le),Dbands(Le))
   Ebands = linspace(-D,D,Le,mesh=de)
   Dbands = dens_bethe(Ebands,D)*de
   !
   !EDIpack: Set impurity Hamiltonian
   call ed_set_hloc(Hloc)
\end{lstlisting}
\end{minipage}
%
\begin{minipage}[t]{0.49\linewidth}
\textbf{C++}
\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
#include <edipack_cbindings.h>
using namespace std;
//...
//Main variables
int Le = 1000;
int iloop = 0;
double wmixing = 0.5;
double D = 1.0;

@@

//Locally defined functions: de = 2*D/Le
Ebands = linspace(-D,D,Le);
Dbands = dens_bethe(Ebands,D,de);

@@

The first two steps are handled directly by \NAME routines, while during the subsequent steps the 
 control returns to the user, who must implement the algebraic updates required to 
close the self-consistency loop and optimize the bath.
Given the critical importance of this optimization, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
Alternative optimization methods can also be employed as 
needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
An example of implementation is provided in the following listings.
